### 2023-03-09 manuscript.tex
Removing duplicated table. [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/388ca7cf852b78a84a8e8b3411f1243976ed978b.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/388ca7cf852b78a84a8e8b3411f1243976ed978b/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4378560886

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/45bcf9513abb9e8e2c4d9134d4bceb88a8696810/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/45bcf9513abb9e8e2c4d9134d4bceb88a8696810}{SORTEE-Github-Hackathon/manuscript@45bcf95}
on March 8, 2023.

@@

  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0627}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0528}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0281}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0281}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0380}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0528}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.1799}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.1683}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.2558}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.1337}}@{}}
\caption{A comparison of technologies commonly used for collaborating on research in Ecology and Evolutionary Biology. In the first column, we group platforms for collaboration into broad guilds. The second column lists the platform for collaboration. The remaining columns indicate whether the platform for collaboration includes certain features. \label{tbl:compare}}\label{tbl:compare}\tabularnewline
Backup (cloud)
Free plan available
Permanent (DOI)
\endfirsthead
Backup (cloud)
Free plan available
Permanent (DOI)
Multi-tool & GitHub & yes & yes & yes & no & Broadly used free version. Advanced features are provided for free to students and education professionals. & A DOI can only be obtained when integrating to other services that can mint DOI (e.g., Zenodo, OSF). & 100MB per file, 500MB per private repository (2GB for paid accounts). 100GB for public repositories. Larger files (up to 2GB) can be attached to releases & N/A \\
Multi-tool & Open Science Framework & yes & yes & yes & yes & yes & yes & 25GB for private projects, up to 5GB per file, plus partner add-ons, 50GB for public projects & yes \\
Long-term (public) data repositories & PANGAEA & yes & yes & yes & no & yes & yes & 10 GB free & no \\
Long-term (public) data repositories & Zenodo & after published & after published & yes & no & yes & yes & 50 GB per dataset & yes \\
Long-term (public) data repositories & Dryad & after published & after published & yes & no & some journals cover cost & yes & 300 GB per publication & Can link to individual files (not entire repository), thus not fully integrated \\
Long-term (public) data repositories & Figshare & yes & yes & yes & no & yes & yes & 20 GB free, up to 5 TB & yes \\
Temporary (personal) drive storage & Google Drive & yes & yes & yes & yes & limited free version \& paid & no & 15GB free, up to 100GB with Google One & yes \\
Temporary (personal) drive storage & Box & limited & yes & yes & yes & no & no & Unlimited total size for subscription & yes \\
Temporary (personal) drive storage & DropBox & limited & yes & yes & yes & limited free version \& paid & no & 2GB free & yes \\
Temporary (personal) drive storage & OneDrive and the Office Suite & yes & yes & yes & yes & limited free version \& paid & no & 5 GB free, up to 1TB paid & yes \\
Collaborative code/text editors & Overleaf (online latex editor) & yes & yes & yes & yes & yes & no & 1MB for individual .tex, 50MB for individual files, unlimited project size & yes \\
Collaborative code/text editors & Jupyter Notebook & yes & ? & yes & with Colab & yes & no & via Binder: no hard limit, but suggests no files \textgreater100MB, can also store on GitHub or Google Colab & yes \\
Collaborative code/text editors & HackMD & yes & yes & yes & yes & limited free version \& paid & no & 3 documents free, private invitee limits & yes \\

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-s91uGRZ2}{}}%
\emph{About code owners}. (n.d.). GitHub Docs. Retrieved March 8, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/managing-your-repositorys-settings-and-features/customizing-your-repository/about-code-owners}

\leavevmode\vadjust pre{\hypertarget{ref-1Co6ZZjF1}{}}%
\emph{About large files on GitHub}. (n.d.). GitHub Docs. Retrieved March 8, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/working-with-files/managing-large-files/about-large-files-on-github}

\leavevmode\vadjust pre{\hypertarget{ref-RhBKe0MG}{}}%
\emph{About Projects}. (n.d.). GitHub Docs. Retrieved March 8, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/issues/planning-and-tracking-with-projects/learning-about-projects/about-projects}

\leavevmode\vadjust pre{\hypertarget{ref-TOsASkn5}{}}%
\emph{Adding a license to a repository}. (n.d.). GitHub Docs. Retrieved March 8, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/communities/setting-up-your-project-for-healthy-contributions/adding-a-license-to-a-repository}

@@

\leavevmode\vadjust pre{\hypertarget{ref-xbM3u93u}{}}%
Braga, P. H. P., Peres-Neto, P., \& Kembel, S. (2023). \emph{Data for: Historical and contemporary processes drive global phylogenetic structure across geographical scales: Insights from bat communities} (Version 7) {[}Data set{]}. Dryad. \url{https://doi.org/10.5061/dryad.rjdfn2zgj}

@@

\leavevmode\vadjust pre{\hypertarget{ref-6CMMeSeD}{}}%
Bryan, J., \& TAs, T. S. 545. (n.d.). \emph{STAT 545}. Retrieved March 8, 2023, from \url{https://stat545.com/}

\leavevmode\vadjust pre{\hypertarget{ref-lx49NGto}{}}%
\emph{Connect GitHub to a Project - OSF Support}. (n.d.). Retrieved March 8, 2023, from \url{https://help.osf.io/article/211-connect-github-to-a-project}

\leavevmode\vadjust pre{\hypertarget{ref-T03Api6e}{}}%
\emph{Continuous Integration and Delivery}. (n.d.). CircleCI. Retrieved March 8, 2023, from \url{https://circleci.com/}

@@

\leavevmode\vadjust pre{\hypertarget{ref-NUXbp429}{}}%
\emph{Features • GitHub Actions}. (n.d.). GitHub. Retrieved March 8, 2023, from \url{https://github.com/features/actions}

@@

\leavevmode\vadjust pre{\hypertarget{ref-ZvrOcg9w}{}}%
Hester, J. B., the STAT 545 TAs, Jim. (n.d.). \emph{Let's Git started \textbar{} Happy Git and GitHub for the useR}. Retrieved March 8, 2023, from \url{https://happygitwithr.com/}

@@

\leavevmode\vadjust pre{\hypertarget{ref-nDkLlAch}{}}%
\emph{Openscapes}. (n.d.). Retrieved March 8, 2023, from \href{https:////}{//}

@@

\leavevmode\vadjust pre{\hypertarget{ref-oGbKxHzj}{}}%
\emph{Using Git and GitHub}. (n.d.). Retrieved March 8, 2023, from \url{https://www.overleaf.com/learn/how-to/Using_Git_and_GitHub}

>>>>

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/388ca7cf852b78a84a8e8b3411f1243976ed978b/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/388ca7cf852b78a84a8e8b3411f1243976ed978b}{SORTEE-Github-Hackathon/manuscript@388ca7c}
on March 9, 2023.

@@

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-s91uGRZ2}{}}%
\emph{About code owners}. (n.d.). GitHub Docs. Retrieved March 9, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/managing-your-repositorys-settings-and-features/customizing-your-repository/about-code-owners}

\leavevmode\vadjust pre{\hypertarget{ref-1Co6ZZjF1}{}}%
\emph{About large files on GitHub}. (n.d.). GitHub Docs. Retrieved March 9, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/working-with-files/managing-large-files/about-large-files-on-github}

\leavevmode\vadjust pre{\hypertarget{ref-RhBKe0MG}{}}%
\emph{About Projects}. (n.d.). GitHub Docs. Retrieved March 9, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/issues/planning-and-tracking-with-projects/learning-about-projects/about-projects}

\leavevmode\vadjust pre{\hypertarget{ref-TOsASkn5}{}}%
\emph{Adding a license to a repository}. (n.d.). GitHub Docs. Retrieved March 9, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/communities/setting-up-your-project-for-healthy-contributions/adding-a-license-to-a-repository}

@@

\leavevmode\vadjust pre{\hypertarget{ref-xbM3u93u}{}}%
Braga, P. H. P., Kembel, S., \& Peres-Neto, P. (2023). \emph{Data for: Historical and contemporary processes drive global phylogenetic structure across geographical scales: Insights from bat communities} (Version 9) {[}Data set{]}. Dryad. \url{https://doi.org/10.5061/dryad.rjdfn2zgj}

@@

\leavevmode\vadjust pre{\hypertarget{ref-6CMMeSeD}{}}%
Bryan, J., \& TAs, T. S. 545. (n.d.). \emph{STAT 545}. Retrieved March 9, 2023, from \url{https://stat545.com/}

\leavevmode\vadjust pre{\hypertarget{ref-lx49NGto}{}}%
\emph{Connect GitHub to a Project - OSF Support}. (n.d.). Retrieved March 9, 2023, from \url{https://help.osf.io/article/211-connect-github-to-a-project}

\leavevmode\vadjust pre{\hypertarget{ref-T03Api6e}{}}%
\emph{Continuous Integration and Delivery}. (n.d.). CircleCI. Retrieved March 9, 2023, from \url{https://circleci.com/}

@@

\leavevmode\vadjust pre{\hypertarget{ref-NUXbp429}{}}%
\emph{Features • GitHub Actions}. (n.d.). GitHub. Retrieved March 9, 2023, from \url{https://github.com/features/actions}

@@

\leavevmode\vadjust pre{\hypertarget{ref-ZvrOcg9w}{}}%
Hester, J. B., the STAT 545 TAs, Jim. (n.d.). \emph{Let's Git started \textbar{} Happy Git and GitHub for the useR}. Retrieved March 9, 2023, from \url{https://happygitwithr.com/}

@@

\leavevmode\vadjust pre{\hypertarget{ref-nDkLlAch}{}}%
\emph{Openscapes}. (n.d.). Retrieved March 9, 2023, from \href{https:////}{//}

@@

\leavevmode\vadjust pre{\hypertarget{ref-oGbKxHzj}{}}%
\emph{Using Git and GitHub}. (n.d.). Retrieved March 9, 2023, from \url{https://www.overleaf.com/learn/how-to/Using_Git_and_GitHub}
